---
title: "Lab 2"
author: "Tracie-Lynn Lamoreux, Macy Schanbacher"
date: "2023-03-02"
output: html_document
---

```{r setup, include=FALSE}
choco<- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
library(ggplot2)
library(tidyverse)
head(choco)
nrow(choco)
```

1. What is the overall number of chocolate bars rated?
```{r}
nrow(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports
```{r}
ggplot(data=choco,aes(y=Rating))+ geom_bar()+ facet_wrap(~Review.Date)
```
Questions set 2:
1. For each of the questions below provide at least one graphic as a basis for your answer.
a. How are ratings distributed? Draw a histogram of ratings and describe it.

```{r}
ggplot(data=choco,aes(y=Rating))+geom_histogram(bins=15)+coord_flip()
```

b. Do ratings depend on the cocoa percentage of a chocolate bar?
```{r}
choco$Cocoa.Pct<- as.factor(choco$Cocoa.Pct)
ggplot(data=choco, aes(x=Cocoa.Pct,y=Rating))+geom_boxplot()+coord_flip()
```
c. How do ratings compare across different company locations? Focus on the three locations with the most ratings.
```{r}
df<- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada")) 
ggplot(data=df,aes(x=Company, y= Rating))+geom_boxplot()+coord_flip()
```

Macy's Question
What type of choco bean has the highest rating out of the top three bean types (Trinitario, Criollo, Forastero) ?
```{r}
bean_types = dplyr::filter(choco, Bean.Type %in% c("Trinitario", "Criollo", "Forastero"))
ggplot(bean_types, aes(x = Bean.Type, y = Rating)) + geom_boxplot()
```
In this graph we see that there is not much of a difference between the type of bean used and the rating. Most of the ratings fall in between the 3 - 3.5 ratings. The Forastero bean is very slightly lower than the others but the ratings for the Criollo and Trinitario beans are very similar. 

